\documentclass[]{rahulworld-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Satya Sai Sundar Keerthi}\\
\end{large}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{17pt}
 


\section{Links} 
\noindent\rule{5cm}{0.4pt}

 \faGithub \enspace\href{https://github.com/sundar68}{Github} \\
 \\
 \faUser \enspace \href{https://sundar68.github.io/three}{Portfolio} \\
 
\faLinkedin \enspace\href{https://www.linkedin.com/in/keerthi-satya-sai-sundar-900a0b196}{Linkedin} \\

\faArrowCircleRight \enspace\href{https://www.hackerrank.com/sundarkeerthi111}{Hackerrank} \\

\faArrowCircleRight \enspace\href{https://leetcode.com/sundar68/}{Leetcode} 
\vspace{6pt}
\vspace{6pt}
\vspace{6pt}
\vspace{6pt}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}

\subsection{\custombold{Languages}}
\vspace{3pt}
C, C++, Python,\\
HTML, CSS.
\vspace{10pt}
\subsection{\custombold{Developer Tools}}
\vspace{3pt}
VS Code, \\
Google Collab.
\vspace{10pt}
\subsection{\custombold{Frameworks}}
\vspace{3pt}
SQL, React JS,\\
 Github.\\
\vspace{6pt}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithms\\
OOP's\\
Web Designing\\
DBMS\\
Discrete Mathematics\\
\vspace{6pt}

\sectionsep

\section{Languages}
\noindent\rule{5cm}{0.4pt}

English \\
Telugu \\
Hindi 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{BS in Computer ence}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill \faMapMarker \enspace Visakhapatnam, Andhra Pradesh \\
\hspace*{0pt}\hfill \faMobile \enspace +91-7032487794 \\
\hspace*{0pt}\hfill \faEnvelopeO \enspace\textbf{\href{mailto: sundarkeerthi111@gmail.com}{sundarkeerthi111@gmail.com}} \\


\section{Education}
\noindent\rule{12.5cm}{0.4pt}
\cvevent{2019--present}{\custombold{B.Tech. Computer Science and Engineering}}
        {National Institute of Technology}{Silchar, Assam}
\cvitem{CGPA: 8.1}

\cvevent{2017--2019}{\custombold{Senior Secondary (XII)}}
        {Sasi Junior Colloge (BIEAP)}{Velivennu,Andhra Pradesh}
\cvitem{CGPA: 9.94/10  }
\cvevent{2017 passout}{\custombold{Secondary  (X)}}
        {Ravindra Bharathi School }{Tuni, Andhra Pradesh}
\cvitem{GPA: 10/10}


\section{Projects}
\noindent\rule{12.5cm}{0.4pt}


{\customcvproject{\custombold{ENVIROPROMISE}}{\enspace \href{https://github.com/sundar68/enviro}{\faArrowCircleRight}}
 {\begin{itemize}
   \item \textbf{Internship as a frontend developer.}
    \item Built a website from scratch in a team of 3 members.
    \item  Used React JS,HTML,CSS for frontend development and learnt best usage of React hooks.
  \end{itemize}
  }
}
{\customcvproject{\custombold{{PORTFOLIO}}}{ \enspace \href{https://github.com/sundar68/three}{\faArrowCircleRight}}
{\begin{itemize}
  \item Built  a self Portfolio website using React JS. 
  \item Used neumorphic UI design.
  \item \text{\url{https://sundar68.github.io/three/}}
\end{itemize}
}
}



\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\cvevent{05--07/2021}{\custombold{Front End Developer}}
        {Enviropromise}{Hyderabad, Telangana}
\cvitem{ \href{https://drive.google.com/file/d/11th9RjlnkBQfkorg8XykPTCvt_LEwrv0/view?usp=drivesdk}{\custombold{Certificate \faArrowCircleDown}} }
  
\vspace{6pt}





\section{Achivements}
\noindent\rule{12.5cm}{0.4pt}

    	\begin{itemize}
    	 \item Received letter of recommendation from Enviropromise  as honour of my  hardwork. 
    	 \item Solved 200+ problems in leetcode.
          \item Certification of skill Test by Hackerrank in React JS and SQL.Secured 5-star in C, C++ and SQL in Hackerrank. 
          \item Secured 98.6 percentile in JEE mains 2019 and Secured AIR 10500 in JEE advanced.

		\end{itemize}



\end{minipage}
 
\end{document}  \documentclass[]{article}